Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-22 manuscript/manuscript.Rmd
Add some contrast in graphs for printing in bw

word-count: "8,061"

@@

```{r relationship-social, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%", fig.cap="Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO–host government relationships"}
sim_final %>% 
  group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
             x = avg_share, color = persona_trust)) +
  geom_pointrange(size = 0.75, fatten = 1.5,
                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  scale_color_manual(values = clrs_ngo_pairs[[3]], 
                     guide = guide_legend(reverse = TRUE,
                                          override.aes = list(size = 0.25,
                                                              linetype = 0))) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank(),
        legend.key.width = unit(0.5, "lines"))
```

>>>>

word-count: "7,983"

@@

```{r relationship-social, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%", fig.cap="Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO–host government relationships"}
sim_final %>% 
  group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
             x = avg_share, color = persona_trust, shape = persona_trust)) +
  geom_pointrange(size = 0.75, fatten = 1.5,
                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  scale_color_manual(values = clrs_ngo_pairs[[3]], 
                     guide = guide_legend(reverse = TRUE,
                                          override.aes = list(size = 0.25,
                                                              linetype = 0,
                                                              shape = c(20, 17)))) +
  scale_shape_manual(values = c(17, 20), guide = FALSE) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank(),
        legend.key.width = unit(0.5, "lines"))
```
